\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-08-05 popl-2019-journal-v/discussion.tex
[POPLjv] Rewrite continuation/exception discussion

  We conjecture that \stktokens{} can support a limited form of continuations and exceptions.
  Specifically, the continuations and exceptions would be passed to the callee as sealed code capabilities.
  In order for the continuations and exceptions to work with the stack, they would have to be sealed with the return seals.
  \dominique{I'm not convinced that these limitations cannot be avoided. Perhaps we should keep this discussion more tentative?}
  This requirement puts two strong limitations on continuations and exceptions.
  First of all, they can be used by the immediate callee, but they cannot be used in subsequent calls made by the callee (assuming they use \stktokens{}).
  The problem is that the callee would have to take up part of the stack for their local stack frame.
  This would break up the return token that should be used with the continuation (or exception).
  If the callee really needs to pass on the continuation, then they would have to construct a wrapper that unravels the stack and restores the necessary return token.
  Second, a call that passes continuations or exceptions in this way has to pass the same continuations and exceptions in every call.
  The problem is that just like the return code capability, the continuation and exception capabilities are non-linear.
  This means that a callee can store them for subsequent calls preventing us from using different continuations and exceptions for different calls.

  \dominique{Also: should we mention the limited additional control flow we seem to get if we omit the stack base check (where  adversaries can use a kind of non-preemptive multi-threading)?}

>>>>

  We have not investigated support for continuations and exceptions in \stktokens{} thoroughly but believe they are supported.
  The continuations and exceptions could plausibly be implemented similarly to return pointers, i.e.\ as sealed code capabilities.
  The exception capability would point to a piece of code handling the specific exception, and one would cast an exception by invoking the exception capability.
  The continuations and exceptions would be sealed with the return capability allowing them to be used with the appropriate encapsulated stack frame.
  The stack is crucial to \stktokens{}, and it must be unravelled as an exception falls through calls.
  One way to handle stack unravelling is to make the code responsible for unravelling its own stack frame.
  For a piece of code that wants to pass on a continuation, it would have to pass on a capability for a piece of code that unravels the stack and uses the continuation.
  Alternatively, it may be possible to have a piece of central trusted code that does the stack unravelling.
